Notes & Ideas

### 2018-11-30 course_notes.Rmd
Update

# Session 3 (Nov. 12, 2018)
I have 11,000 comments from TAs on student reports. Process for bringing in the tidied data and structuring it for analysis is not done, but is coming along.

I want to sort TA comments into topic groups more or less automatically, using pre-defined criteria. What are the options?

@@

Found this:  
"In text mining, we often have collections of documents, such as blog posts or news articles, that we’d like to divide into natural groups so that we can understand them separately. Topic modeling is a method for unsupervised classification of such documents, similar to clustering on numeric data, which finds natural groups of items even when we’re not sure what we’re looking for."

Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model. It treats each document as a mixture of topics, and each topic as a mixture of words. This allows documents to “overlap” each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language.

The approach is described here:
	https://www.tidytextmining.com/topicmodeling.html

Challenge is that my groups are **already based on the existing coding book.** The individual groups are already labeled. LDA clusters items based on its own analysis.

@@

# Session 4 (Dec. 3, 2018)
Looking at Jerid's Intro to Statistical Thinking clarified some issues in my approach. I definitely need to be thinking about this problem more in terms of unsupervised exploration.

That leads to my follow-up question: training with 80% seems excessive. If there is a large dataset, is there any cost or benefit to splitting to 33/33/34%, or even 25% x 4? The 80/20 and 60/20/20% seem out of balance, but there is probably logic I do not see.

In the exploration phase, is re-sampling such a major concern?

@@

**Confidentiality Problem**
My initial dataset contains confidential information that needs to be de-identified. How do I convert the data so it can be displayed on a public site?

@@

**What Are the Primary Data Keys For Structuring the Dataset?**
These are values that are present already in the dataset.

*record.id*  
Column is a semester ID and 5-digit number, like sp18.00001. This particular record.id indicates the data line is from Spring 2018 CSV file, and is line 00001 of the data table. This should be the unique primary key value for each record. Once assigned, it should not change.

*report.id*  
Format is R\_nnn(...). The string is assigned to each entry made in Qualtrics. This particular string is assigned when a report is collected by our system. It is anonymous, and serves as a unique id for each REPORT document that we collect.

*student*  
The email address of the SUBMITTING STUDENT. Unique to each student, and assigned by WFU. The email address connects multiple reports to a SINGLE STUDENT AUTHOR. It is NOT confidential though, so needs to be switched out.

*ta*  
The name of the TA assigning scores. Unique to instructor, and connects multiple reports scored by SINGLE TA. Again it is NOT confidential, so also needs to be switched out.

@@

**Lagniappe**
Maybe it is just me, but I've been struggling with some of the outside instructional materials becuase they use generic terms in ways that make code structure more confusing.

@@

>Thank you x^y times over for the Regex101 link! Getting Regex right has been a pain for me! This greatly simplifies the process.

**Miscellaneous To Do**

* Need to review map, cast and bind commands again. Not sticking in my head.
* Try visualizing the 2-D array of the TA comments as a mosaic plot.

>>>>

# Session 3 (Nov. 12, 2018)
I have 11,000 comments from TAs on student reports. Working out a process for bringing in the tidied data and structuring it for analysis is not finished, but is coming along. Some of the challenges and questions I have are outlined in Session 4.

While learning the coding, I have been thinking about how to approach the larger problem once data are in a reasonable form. I want to sort TA comments into topic groups more or less automatically, using pre-defined criteria. What are my options?

@@

I found this summary, and a description of the approach at
[https://www.tidytextmining.com/topicmodeling.html]():

>"In text mining, we often have collections of documents, such as blog posts or news articles, that we’d like to divide into natural groups so that we can understand them separately. Topic modeling is a method for unsupervised classification of such documents, similar to clustering on numeric data, which finds natural groups of items even when we’re not sure what we’re looking for.

>"Latent Dirichlet allocation (LDA) is a particularly popular method for fitting a topic model. It treats each document as a mixture of topics, and each topic as a mixture of words. This allows documents to “overlap” each other in terms of content, rather than being separated into discrete groups, in a way that mirrors typical use of natural language."

My challenge is that LDA clusters items based on its own analysis. My groups are already sorted based on the **existing coding book.** The individual groups are already labeled.

@@

# Session 4 (Dec. 3, 2018)
Looking at Jerid's *Intro to Statistical Thinking* clarified some points in my approach. I definitely need to be thinking about this problem more in terms of unsupervised exploration. It did raise some follow-up questions:

*  A training set with 80% of the data seems excessive. If there is a large dataset, is there any cost or benefit to splitting to 33/33/34%, or even 25% x 4? The 80/20 and 60/20/20% also seems out of balance, but there is probably logic I do not see. 
*  In the exploration phase, is re-sampling such a major concern?

**Separate note:** thank you many times over for the Regex101 link! Writing regex correctly has long been a pain for me! This greatly simplifies the process.

@@

####Confidentiality Problem
My initial dataset contains confidential information that needs to be de-identified. How do I convert the data so it can be displayed on a public site?

@@

####Primary Data Keys For Structuring the Dataset?
These are values that are present already in the dataset.

*record.id*  
>Column is a semester ID and 5-digit number, like sp18.00001. This particular record.id indicates the data line is from Spring 2018 CSV file, and is line 00001 of the data table. This should be the unique primary key value for each record. Once assigned, it should not change.

*report.id*  
>Format is R\_nnn(...). The string is assigned to each entry made in Qualtrics. This particular string is assigned when a report is collected by our system. It is anonymous, and serves as a unique id for each REPORT document that we collect.

*student*  
>The email address of the SUBMITTING STUDENT. Unique to each student, and assigned by WFU. The email address connects multiple reports to a SINGLE STUDENT AUTHOR. It is NOT confidential though, so needs to be switched out.

*ta*  
>The name of the TA assigning scores. Unique to instructor, and connects multiple reports scored by SINGLE TA. Again it is NOT confidential, so also needs to be switched out.

@@

####Lagniappe
Maybe it is just me, but I've been struggling with some of the outside instructional materials becuase they use generic terms in ways that make code structure more confusing.

@@

####Miscellaneous To Do
* Need to review map, cast and bind commands again. Not sticking in my head.
* Try visualizing the 2-D array of the TA comments as a mosaic plot.
